On the Dynamics of Anthropomorphism in Robotics

### 2013-06-26 dynamics-anthropomorphism.tex
Proof-reading, added several 'fixme' all over the place

	The essence of anthropomorphism is perceiving human-like characteristics in either real or imagined non-human agents. According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance (such as a religious agent believed to look human-like), emotional states perceived to be uniquely human, or inner mental states and motivations. Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices". Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light of these agents.

@@

	In this context, anthropomorphism has received remarkable attention in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI). Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}. The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}. The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.

@@

	However, not everything labeled as "anthropomorphism" really is anthropomorphism.	It is true that there are several different, partially even conflicting understandings of anthropomorphism, across and within disciplines \cite{duffy_anthropomorphism_2002}. Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism (in psychology) by explaining what it is \textit{not}. The authors list four things that anthropomorphism does not include: First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable. Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic. Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate. A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.

@@

	Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or humans. At this point, anthropomorphic design enters the stage. The anthropomorphic design of a robot encourages people to reason about this unfamiliar system as if it were a human. To increase this tendency, robots are designed with anthropomorphic forms (human-like forms or lifelike forms, in the broader sense), or are able to display and use human-social behavior.

@@

	The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}. There is no single accepted definition. Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape'). It can be understood as people's tendency to think of objects as if they had human characteristics, and consequently, attribute / ascribe specific human characteristics to these non-human entities and artifacts (including animals, and robots) \cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}. Apart from anthropomorphism there is also \textbf{animism}, the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}. Often synonymously used to animism is \textbf{zoomorphism}, which describes the case when non-lifelike objects are associated with animalistic attributes, excluding human-specific traits. Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}. \footnote{The inverse process, dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986} also exists.}

	Commonly, anthropomorphism can also be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being. The phenomenon of personifying something has ancient roots, \textit{e.g.} in mythology but also in storytelling. Already in prehistoric artworks and illustrations zoomorphic (animal-shaped) or anthropomorphic shapes were used to represent natural forces or great spirits, for instance. A more recent example is Milo Winter's illustration from 1919, \textit{"The North Wind and the Sun"} (Figure \ref{fig:1}), in which both north wind and sun are given a human face (anthropomorphized). Similarly, when parents explain their children about nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would cry when it rains. More generally, a possible explanation for why people anthropomorphize is that by doing so, the subject is made graspable, understandable, somehow predictable, and one could feel more empathetic toward it. For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them \cite{eddy_attribution_1993}. Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners \hl{references!}.

@@

	According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize. The first one explains anthropomorphism from the design of the artifact (anthropomorphic form in the design). It assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it. In fact, from early childhood on, humans are inherently well-trained to perceive life \cite{epley_seeing_2007}. Schmitz \cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance can have an important impact on the overall perception of an object. The basic assumption here is that if an artifact appears much like a human it is likely to be treated similar to a human. If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by a robot, and apply human-human social schemas and norms to these interactions.

	The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does. According to v. Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings"} \cite{hegel_understanding_2008}. This is consistent with the \hl{familiarity thesis (18)} \cite{hegel_understanding_2008} which claims we understand the world based upon a mental model of the world that we are most familiar with. Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them. This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}. A theory of  mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}. If a system behaves much like a human being (e.g. emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref? Schmitz?}. In turn, people's estimation of a robot's `knowledge' and its capabilities / abilities affects the way they relate to it. Research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.

@@

	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from (developmental) psychology. The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in (developmental) psychology. Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}. In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}). Asked to describe what they observed, interestingly, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
% figure caption is below the figure
 \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
 \label{fig:animacy_attribution}       % Give a unique label
 \end{figure}

@@

	Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant  of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents. One basic reasons for this are a person's physical constraints of being a human and nothing else. Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental states. \footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism. See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents. This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.

	Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}. \textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)} about one's environment and the agents that inhabit it. According to Epley \textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment. They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
	\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents. Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized hon-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}. According to Epley \textit{et al.}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment. Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.

@@

	Anthropomorphism is a commonly observed phenomenon in human-robot interaction. Studies showed that there are people who directly talk to their robot (even if it does not recognize speech), give it a name, greet it, wonder about its intentions or actions \cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}. It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or their AIBO robotic dog \cite{friedman_hardware_2003}. However, people's tendency to anthropomorphize technologies has not only been observed with robots but described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}. Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields. What makes anthropomorphism special in robotics, is probably related to the (unique) characteristics of robots in contrast to other technologies. Robots are embodied, physical agents, autonomously acting right next to us, and able to respond intelligently to us and the environment. These are factors that seem to facilitate anthropomorphism, due to the nature of the phenomenon and its origins itself. In robotics, anthropomorphism is further encouraged through specific anthropomorphic design of a robot. But what is the interest, which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots? Why does anthropomorphism seem to be so important in robotics? There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}. More concretely, it has been found that the appearance and function of a \hl{product (research in marketing?)}) impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}. Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}. Studies have further shown that perceived similarity between the user and the robot influences the intense of the participants' attributions towards the robot. Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.

@@

\begin{tikzpicture}

@@

\caption{Dynamics of anthropomorphism. We distinguish three main phases:
\emph{initialization}, \emph{familiarization} and \emph{stabilization}. In the
pre-interaction phase, users build an \emph{initial capital of
anthropomorphism} (ICA). Once the interaction starts, the level of
anthropomorphism increases due to the \emph{novelty effect}, and then decreases
to reach a \emph{stabilized level of anthropomorphism} (SLA).
During the interaction, unpredicted behaviors of the robot (\emph{disruptive
behaviors}) locally increase the level of anthropomorphism.}
\label{fig:dynamics}
\end{figure*}

@@

Why do we think that anthropomorphic inferences are likely to change over time and with growing experience a person has with a robot? The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self). The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}. According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation. This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation. As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time. First, because of the evolved knowledge about it, and second because one has familiarized oneself with it. Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.

@@

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review \cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
these findings in a specific section!}, we believe that anthropomorphic effects in HRI are not always the same but evolve over time, along with growing interaction
and experience with the robot, similar to how relationships among people evolve over time \hl{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.} \cite{kanda_interactive_2004} also hypothesized that people's attitude toward technological artifacts and their relationship with them would evolve over time, and they were among the first who described \textit{novelty effects} during a long-term study with an interactive robot in a school.

The model of anthropomorphism we propose (Figure~\ref{fig:dynamics}) represents
how the level of anthropomorphic effects (\ie observable manifestations of
anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
long-term human-robot interaction. By long-term interaction, we mean direct
(non-mediated), repeated interaction with the same robot, over (at least) several
days. The nature of the interaction (goal-directed, entertainment, etc.) may vary.

The model uses a \emph{normalized} level of anthropomorphic effects: because
anthropomorphic effects are not quantified on an absolute scale, we present
them as a normalized value, that span from a minimum (no anthropomorphic
effects) to a maximum (corresponding to the novelty effect peak on
Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic effects
is strongly correlated to the human, the robot and other factors we introduce
below. Hence, the model we propose only focuses on the general \emph{shape} of
the level of anthropomorphism over time, \ie the general dynamics of
anthropomorphism.

The model takes into account the duration of the interaction, the nature of the
interaction, as well as acquired experience and familiarization mechanisms: We
also propose to formally introduce a so-called \emph{novelty effect} that
models the first phase of human-robot interaction, and during which specific
anthropomorphic effect are observed.

@@

First, the \emph{initialization} phase. During this short phase (from a couple
of seconds to a couple of hours), we observe an increased level of
anthropomorphism, from an \emph{initial capital of anthropomorphism}
(detailed in the next section) and a peak of anthropomorphic manifestations
that corresponds to the maximum of the \emph{novelty effect}.
Section~\ref{sec:initialization} details this first phase.

The second phase, \emph{familiarization}, lasts longer (up to several days) and
models the process of the human getting acquainted to the robot: by observation
and interaction, the human builds a model of the robot's behavior that allows
him/her to predict the robot's actions. We observe a decrease of
anthropomorphic effects during this phase, that we explain by the acquired
ability to predict the behavior of the robot: the initial apparent behavioral
complexity vanishes, and the robot is considered more and more as \hl{a machine (Julia: I would rather say "a tool")}.
Section~\ref{sec:familiarization} discusses the second phase.

>>>>

The essence of anthropomorphism is perceiving human-like characteristics in either real or imagined non-human agents. According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance (such as a religious agent believed to look human-like), emotional states perceived to be uniquely human, or inner mental states and motivations. Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices". Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light\fxnote{in light?} of these agents.

@@

In this context, anthropomorphism has received remarkable attention\fxnote{contradict with intro} in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI). Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}. The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references}\fxnote{Rosenthal is not enough?} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}. The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.

We furthermore use in this article \emph{anthropomorphic effects} to denote the
observable correlates of anthropomorphism. These include, amongst others,
verbal behaviors (like the use of pronouns ``he/she''), kinesics (like hugging
the robot) or anticipation of certain robot's actions.

@@

However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism. Different, even partially conflicting, understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}. Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}. The authors list four things that anthropomorphism does not include: First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable. Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic. Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate. A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents\fxfatal{End of paragraph is unclear. We need to reformulate}.

@@

Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or humans. This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are designed with anthropomorphic forms (human-like forms or lifelike forms, in the broader sense), or are able to display and use human-social behavior.

@@

The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}. There is no single accepted definition\fxfatal{already said before}. Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape'). It can be understood as people's tendency to think of objects as if they had human characteristics, and consequently, attribute / ascribe specific human characteristics to these non-human entities and artifacts (including animals, and robots) \cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}. Apart from anthropomorphism there is also \textbf{animism}, the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}. Often synonymously used to animism is \textbf{zoomorphism}, which describes the case when non-lifelike objects are associated with animalistic attributes, excluding human-specific traits. Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}. \footnote{The inverse process would be called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986}.}

Commonly, anthropomorphism can also be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being. The phenomenon of personifying something has ancient roots, \textit{e.g.} in mythology but also in storytelling. In prehistoric artworks and illustrations, zoomorphic (animal-shaped) or anthropomorphic shapes were already used to represent natural forces or great spirits, for instance. A more recent example is Milo Winter's illustration from 1919, \textit{"The North Wind and the Sun"} (Figure \ref{fig:1}), in which both north wind and sun are given a human face (anthropomorphized). Similarly, when parents explain their children about nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would cry when it rains. More generally, an explanation for why people anthropomorphize is that by doing so, the subject is made \emph{graspable}, \emph{understandable}, \emph{predictable}, and one feel \emph{more empathetic} toward it\fxnote{important part. Emphasize this 4 facets, eg by saying we build on top of them}. For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them \cite{eddy_attribution_1993}. Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners \hl{references!}.

@@

\fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
	According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize. The first one explains anthropomorphism from the design of the artifact (anthropomorphic form in the design). It assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it. In fact, from early childhood on, humans are inherently well-trained to perceive life \cite{epley_seeing_2007}. Schmitz \cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance can have an important impact on the overall perception of an object. The basic assumption here is that if an artifact appears much like a human, it is likely to be treated similar to a human. If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by a robot, and apply human-human social schemas and norms to these interactions.

    The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does. According to v. Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings"} \cite{hegel_understanding_2008}. This is consistent with the \hl{familiarity thesis (18)} \cite{hegel_understanding_2008} which claims we understand the world based upon a mental model of the world that we are most familiar with. Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them. This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}. A theory of  mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}. If a system behaves much like a human being (\eg emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref? Schmitz?}. In turn, people's estimation of a robot's knowledge model and its capabilities affects the way they relate to it. Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.

@@

	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from developmental psychology. The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in developmental psychology. Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}. In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}). Asked to describe what they observed, interestingly, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
% figure caption is below the figure
 \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
 \fxnote{wrap text around this figure?}
 \label{fig:animacy_attribution}       % Give a unique label
 \end{figure}

@@

	Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant  of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents. One basic reasons for this are a person's physical constraints of being a human and nothing else. Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state. \footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism. See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents. This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.

    Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}. \textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}\fxfatal{important! move/copy that to the 'model' section or discussion} about one's environment and the agents that inhabit it. According to Epley \textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment. They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.

	\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents. Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}. According to Epley \textit{et al.}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment. Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.

@@

Anthropomorphism is a commonly observed phenomenon in human-robot interaction. Studies showed that there are people who directly talk to their robot (even if it does not recognize speech), give it a name, greet it, wonder about its intentions or actions \cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}. It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or their AIBO robotic dog \cite{friedman_hardware_2003}. People's tendency to anthropomorphize technologies has besides been described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}. Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields, which is probably related to the embodied nature of robots. They are physical agents, autonomously acting right next to us, and also designed to interact intelligently with us and the environment. Besides, anthropomorphism may be further supported by a specific anthropomorphic \emph{design}. But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots? Why does anthropomorphism seem to be so important in robotics? There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}. More concretely, it has been found that the appearance and function of a \hl{product (research in marketing?)}) impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}. Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit confusing...}. Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot. Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.

@@

\begin{tikzpicture}[scale=1.2]

@@

\caption{Dynamics of anthropomorphism. We distinguish three main phases:
\emph{initialization}, \emph{familiarization} and \emph{stabilization},
preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
users build an \emph{initial capital of anthropomorphism} (ICA). Once the
interaction starts, the level of anthropomorphism increases due to the
\emph{novelty effect}, and then decreases to reach a \emph{stabilized level
of anthropomorphism} (SLA).  During the interaction, unpredicted behaviors
of the robot (\emph{disruptive behaviors}) may lead to local increase of the
level of anthropomorphism.}

\label{fig:dynamics}
\end{figure*}

@@

Why do we think that anthropomorphic projections are likely to change over time and with growing experience a person has with a robot? The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self). The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}. According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation. This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation. As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time. First, because of the evolved knowledge about it, and second because one has familiarized oneself with it. Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
/fxfatal{confusing paragraph...needs reformulation. Could also be turned into a section introduction instead of a subsection}

@@

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review previously published~\cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
these findings in a specific section!}, we believe that anthropomorphic effects in HRI are not always the same but evolve over time, along with growing interaction
and experience with the robot, similar to how relationships among people evolve over time \hl{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.} \cite{kanda_interactive_2004} also hypothesized that people's attitude toward technological artifacts and their relationship with them would evolve over time, and they were among the first who described \textit{novelty effects} during a long-term study with an interactive robot in a school.

The model of anthropomorphism we propose (Figure~\ref{fig:dynamics}) represents
how the level of anthropomorphic effects (\ie observable manifestations of
anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
long-term human-robot interaction. By long-term interaction, we mean direct
(non-mediated), repeated interaction with the same robot, over at least several
days. The nature of the interaction (goal-directed, entertainment, etc.) may
however vary.

Anthropomorphism is quantified by a \emph{normalized level of anthropomorphic
effects}: because anthropomorphic effects are not quantified on an absolute
scale, we present them as a normalized value, that spans from a minimum (no
anthropomorphic effects) to a maximum (corresponding to the novelty effect peak
on Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic
effects depends on each unique combinations of human, robot and several other
factors we introduce below, and thus varies. The general \emph{shape} of the
model remains however the same and depicts the level of anthropomorphism over
time, \ie the general dynamics of anthropomorphism.

The model takes into account the duration of the interaction, the nature of the
interaction, as well as acquired experience and familiarization mechanisms. We
also formally introduce a so-called \emph{novelty effect} that
models the first phase of human-robot interaction, during which a specific
increase of anthropomorphic interactions is observed.

@@

First, the \emph{initialization} phase. During this short phase (from a couple
of seconds to a couple of hours), we observe an increased level of
anthropomorphism, from an \emph{initial capital of anthropomorphism}
(detailed in the next section) to a peak of anthropomorphic manifestations
that corresponds to the maximum of the \emph{novelty effect}.
Section~\ref{sec:initialization} details this first phase.

The second phase, \emph{familiarization}, lasts longer (up to several days) and
models the process of the human getting acquainted to the robot: by observation
and interaction, the human builds a model of the robot's behavior that allows
him/her to predict the robot's actions. We observe a decrease of
anthropomorphic effects during this phase, that we explain by the acquired
ability to predict the behavior of the robot: the initial apparent behavioral
complexity vanishes, and the robot is considered more and more as a tool.
Section~\ref{sec:familiarization} discusses the second phase.

The last phase is the \emph{stabilization} phase. The level of anthropomorphic
effects tends to stabilize over a longer time, to reach a \emph{stabilized
level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
effects observed anymore), but it may also remain at a higher level.  This
third phase, as well as the \emph{stabilized level of anthropomorphism}, are
discussed in section~\ref{sec:stabilization} below.
